Datasets

### 2018-08-29 scripts/01-datasets/README.Rmd
add some readme to the datasets
update readmes

---
title: "Datasets"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

All datasets can be downloaded from zenodo using the [00-download_from_zenodo.R](00-download_from_zenodo.R) script.

```{r child='01-real/README.Rmd'}

```

```{r child='02-synthetic/README.Rmd'}

```

>>>>

---
output: github_document
---

# Dataset processing and characterisation

```{r include=FALSE}
library(dynbenchmark)
library(tidyverse)

knitr::opts_chunk$set(echo = FALSE)
```

@@

```{r}
dynbenchmark::render_scripts_documentation()
```

```{r results = 'asis'}
knit_child_readme("01-real")
```

```{r results = 'asis'}
knit_child_readme("02-synthetic")
```

```{r results = 'asis'}
knit_child_readme("05-dataset_characterisation")
```
